Supplementary material for ``An Efficient Forecasting Approach to Reduce Boundary Effects in Real-Time Time-Frequency Analysis''

### 2020-09-10 Notes/BoundEffRed.tex
affilations

\author{Adrien~Meynard, %~\IEEEmembership{Member,~IEEE,}
        Hau-Tieng~Wu
\thanks{A. Meynard and H.-T. Wu are with the Department
of Mathematics, Duke University, Durham,
NC, 27708 USA e-mail: adrien.meynard@duke.edu}}

>>>>

\author{Adrien~Meynard, %~\IEEEmembership{Member,~IEEE,}
        Hau-Tieng~Wu
\thanks{A. Meynard is with the Department
of Mathematics, Duke University, Durham,
NC, 27708 USA.

H.-T. Wu is with the Department of Mathematics and Department of Statistical Science, Duke University, Durham, NC, 27708 USA; Mathematics Division, National Center for Theoretical Sciences, Taipei, Taiwan.

A. Meynard is the corresponding author. e-mail: adrien.meynard@duke.edu
}}

### 2020-09-10 Notes/Supplementary material/SupMat.tex
affilations

\author{Adrien~Meynard, %~\IEEEmembership{Member,~IEEE,}
        Hau-Tieng~Wu
\thanks{A. Meynard and H.-T. Wu are with the Department
of Mathematics, Duke University, Durham,
NC, 27708 USA e-mail: adrien.meynard@duke.edu}}

>>>>

\author{Adrien~Meynard, %~\IEEEmembership{Member,~IEEE,}
        Hau-Tieng~Wu
\thanks{A. Meynard is with the Department
of Mathematics, Duke University, Durham,
NC, 27708 USA.

H.-T. Wu is with the Department of Mathematics and Department of Statistical Science, Duke University, Durham, NC, 27708 USA; Mathematics Division, National Center for Theoretical Sciences, Taipei, Taiwan.

A. Meynard is the corresponding author. e-mail: adrien.meynard@duke.edu}}
